Systematic Design of Optimal Low-Thrust Transfers for the Three-Body Problem \thanks{This research has been supported in part by NSF under the grants CMMI-1243000 (transferred from 1029551), CMMI-1335008, and CNS-1337722.}

### 2017-01-17 manuscript.tex
Add multiple shooting tikz plot
Issue #4

The optimal control formulation presented in this section results in a two point boundary value problem (TPBVP). 
There exist many methods to solve TPBVPs such as gradient, quasilinearization, and shooting methods~\cite{bryson1975,kirk2012}.
Shooting methods are common in astrodynamic trajectory design problems and relatively simple to implement.
In the shooting method, initial conditions are varied such that a terminal constraint is satisfied, similar to the way an archer modifies the bow in order to more accurately strike a target. 
Rather than numerical integration over the entire time interval, multiple shooting segments the interval into several smaller sub-arcs~\cite{stoer2013}.
The multiple shooting method is implemented in this paper which alleviates many of the issues associated with single shooting approaches.
Additional interior constraints are used to ensure a continuous solution.
This has the benefit of decreasing the numerical sensitivity of the final states to changes in the initial conditions along each sub-arc.
% tpbvp is solved using a shooting method (fsolve in matlab)
% determine a design vector X of variables we need to determine
% define a constraint vector G(X) that we need to satisfy
% multiple shooting has interior points of continuity constraints
% sensitivity of terminal state is used to correct the initial condition (cite a book/paper)
% plot of multiple shooting ( stages)
\section{Numerical Example}\label{sec:simulation}
We present two numerical simulations in the Earth-Moon system to demonstrate the transfer procedure.
These simulations enable the spacecraft to depart from the natural dynamics through the use of low-thrust propulsion.
The reachability set on the \Poincare section allows for a straightforward method of determining transfer opportunities.

>>>>

The optimal control formulation presented in this section results in a two point boundary value problem (TPBVP). 
There exist many methods to solve TPBVPs such as gradient, quasilinearization, and shooting methods~\cite{bryson1975,kirk2012}.
Shooting methods are common in astrodynamic trajectory design problems and relatively simple to implement.
In the shooting method, initial conditions are varied such that a terminal constraint is satisfied, similar to the way an archer modifies the bow in order to more accurately strike a target. 
Rather than numerical integration over the entire time interval, multiple shooting segments the interval into several smaller sub-arcs~\cite{stoer2013}.
The multiple shooting method is implemented in this paper which alleviates many of the issues associated with single shooting approaches.
\Cref{fig:multiple shooting} shows a schematic representation of the multiple shooting procedure.

\begin{figure}
	\centering
	\begin{scaletikzpicturetowidth}{1\textwidth}
		\begin{tikzpicture}[scale=\tikzscale]
		    % \draw[help lines] (0,0) grid (20,5) ; %grid

		    \node[label=west:\(\vecbf{x}\)] (x0m) at (0,5) {};
		    \node[] (x1m) at (5,5) {};
		    \node[] (x2m) at (10,5) {};
		    \node[] (x3m) at (15,5) {};
		    \node[] (xnm) at (20,5) {};

		    \node[label=below:\(t_0\)] (t0) at (0,0) {};
		    \node[label=below:\(t_1\)] (t1) at (5,0) {};
		    \node[label=below:\(t_2\)] (t2) at (10,0) {};
		    \node[label=below:\(t_{n-1}\)] (t3) at (15,0) {};
		    \node[label=below:\(t_n\)] (tn) at (20,0) {};

		    % nodes for each subsegment
		    \node[label=left:\(\vecbf{x}_0\)] (x0) at (0,1) {\pgfuseplotmark{*}};

		    \node[label=right:\(\vecbf{x}_1^{-}\)] (x1minus) at (5,2) {\pgfuseplotmark{*}};
		    \node[label=left:\(\vecbf{x}_1^{+}\)] (x1plus) at (5,3) {\pgfuseplotmark{o}};

		    \node[label=right:\(\vecbf{x}_2^{-}\)] (x2minus) at (10,2) {\pgfuseplotmark{*}};
		    \node[label=left:\(\vecbf{x}_2^{+}\)] (x2plus) at (10,3) {\pgfuseplotmark{o}};

		    \node[label=right:\(\vecbf{x}_{n-1}^{-}\)] (x3minus) at (15,2) {\pgfuseplotmark{*}};
		    \node[label=left:\(\vecbf{x}_{n-1}^{+}\)] (x3plus) at (15,3) {\pgfuseplotmark{o}};

		    \node[label=right:\(\vecbf{x}_n\)] (xnminus) at (20,3) {\pgfuseplotmark{*}};
		    % draw axes
		    \draw [<->,thick] (tn.center) -- (t0.center) -- (x0m.center);

		    % draw segement dividers
		    \draw [dashed,thick] (t1.center) -- (x1m.center);
		    \draw [dashed,thick] (t2.center) -- (x2m.center);
		    \draw [dashed,thick] (t3.center) -- (x3m.center);
		    \draw [dashed,thick] (tn.center) -- (xnm.center);

		    % draw markers at each subsegment

		    % draw the subsegments
		    \draw [->] (x0.center) to [bend left=30] (x1minus.center);
		    \draw [->] (x1plus.center) to [bend left=30] (x2minus.center);
		    % dotted lines here
		    \draw[decorate sep={2mm}{10mm},fill] (x2plus.east) to [bend left=30] (x3minus.west);

		    \draw [->] (x3plus.center) to [bend left=30] (xnminus.center);
		\end{tikzpicture}
	\end{scaletikzpicturetowidth}
	\caption{Multiple Shooting method\label{fig:multiple shooting}}
\end{figure}

More detail on how the multiple shooting works
Explain the image
Additional interior constraints are used to ensure a continuous solution.
This has the benefit of decreasing the numerical sensitivity of the final states to changes in the initial conditions along each sub-arc.
% tpbvp is solved using a shooting method (fsolve in matlab)
% determine a design vector X of variables we need to determine
% define a constraint vector G(X) that we need to satisfy
% multiple shooting has interior points of continuity constraints
% sensitivity of terminal state is used to correct the initial condition (cite a book/paper)
% plot of multiple shooting ( stages)
\section{Numerical Example}\label{sec:simulation}
We present two numerical simulations in the Earth-Moon system to demonstrate the transfer procedure.
These simulations enable the spacecraft to depart from the natural dynamics through the use of low-thrust propulsion.
The reachability set on the \Poincare section allows for a straightforward method of determining transfer opportunities.
